When are Fuzzy Extractors Possible?

### 2014-09-29 trunk/info-bounds/FuzzyExtPossibility.tex
moving some proofs to appendix

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
work was sponsored by the Department of the Air Force under Air Force
Contract
\#FA8721-05-C-0002.  Opinions,
interpretations, conclusions and recommendations are those of the author
and
are not necessarily endorsed by the United States Government.  Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that
\[
\forall w, w'\in \mathcal{M}, \dis(w, w')\le t \Rightarrow \Pr[(R, P)\leftarrow \gen(w) \wedge \rep(w', P) =R] \ge 1-\delta
\]
where the probability is taken over the coins of $\gen, \rep$.
\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.  \bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.  The canonical construction is called \emph{sketch-and-extract} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
\[
 \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta
 \] 
where the probability is taken over the coins of $\sketch$ and $\rec$.  
\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness} 
\[
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.\]
Correctness is guaranteed only for the support of $W$.
\item \emph{Security} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.  It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.

@@

If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal in the following result.  
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}
\begin{proof}
Let $W$ be a distribution where $\Hfuzz(W) = \Theta(\log n)$.  This means that there exists a point $m^*\in \mathcal{M}$ such that $\Pr_{w\in W}[\dis (w, m^*)\leq t] \geq 1/\poly(n)$.  Consider the following distinguisher $D$:
\begin{itemize}
\item Input $r, p$.
\item If $\rep(m^*, p) = r$, output $1$.
\item Else output $0$.
\end{itemize}
First note that $|D|$ is of size $\max |\mathcal{M}|+ |\rep|$.  Clearly, $\Pr[D(R, P) = 1]\geq 1/\poly(n) - \delta$, while $\Pr[D(U_\kappa, P)=1 ]= 1/2^{-\kappa}$.  Thus, when $\kappa = \omega(\log n)$:
\[
\delta^D((R, P), (U_\kappa, P))\geq \frac{1}{\poly(n)} -\delta -  \frac{1}{2^{-\kappa}} = 1/\poly(n).
\]
\end{proof}
Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
\lemref{lem:fuzz necessary} still applies.  This is because $D$ only provides an input to the protocol and looks at the output.  This means that fuzzy min-entropy is also a necessary condition for interactive solution.  As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.

@@

We now present a construction for flat distributions.  We universal hashes:

@@

A sufficiently-long universal hash function suffices to construct an information-theoretic fuzzy extractor.  Skoric et al. previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.

@@

\begin{lemma}
Let $W$ be a flat distributions with min-entropy $m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

@@

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.
\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}
\begin{proof}
\textbf{Correctness:}  We begin by arguing correctness.  Let $\ell$ be a parameter describing the number of levels.\footnote{later we will set $\ell = m$ to simplify expressions and obtain the theorem statement.  The proof can be carried out for an arbitrary $\ell$.}  Fix some $w, w'$.  If $\Pr[W=w]\le 2^{-(n+\ell)}$, then $w$ is simply transmitted to $\rec$ and correctness is clear.  Now consider the case when $\Pr[W=w]> 2^{-(n+\ell)}$, let $L_i^*$ be the level of $\Pr[W=w]$.
Let $W^*$ denote the set of elements in $W$ within distance $t$ of $w'$ such that $\forall w \in W^*, \Pr[W^*=w]\in L_i^*$. The size of $W^*$ is at most $B_{t, i, max}$. The choice of $w, w'$ is independent of $\sketch$, so this set is independent of $\mathcal{K}_i$~(it does effect the value of $i$ but not the particular outcome from $\mathcal{K}_i$).  Note $\rec$ will never output $\perp$ as the correct $w$ will match the hash.  The probability that another element $w^*$ is:
\begin{align*}
\Pr[\exists w^* \in W^* |w^* \neq w \wedge F(K, w^*) = F(K, w)] &\le \sum_{w^*\in W^* | w^*\neq w} \Pr[F(K, w^*) = F(K, w)] \\
 &= \sum_{w^*\in W^* | w^*\neq w} \frac{1}{|R_i|} \le \frac{|B_{t, i, max}|-1}{|R_i|} = \delta
\end{align*}
Where the inequality proceeds by union bound, the first equality proceeds by the universality of $F$, and the second inequality proceeds by noting the number of neighbors is bounded by $|B_{t, i, max}|$.

@@

The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.  The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.  More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively. We will formulate this as a two player game.\footnote{We denote the outcome of the game as a reward to each player.  This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.  This is to apply results from game theory.}

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}

%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
$W \leftarrow \mathcal{W}$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}

The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.  In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.  These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.

\begin{lemma}
\label{lem:quant switch fuzz}
Let $\mathcal{V}$ be a family of distributions.  Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.  Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.  Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-fuzzy extractor.\footnote{The other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
\end{lemma}

Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.  Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.  We can think of the description of $W$ as side-information or leakage to the adversary.  The system designer, however never sees the particular outcome $W$.  This asymmetry will form the basis of our negative results in the next subsection.

\begin{corollary}
\label{cor:no fuzz for dist}
Let $\mathcal{V}$ be a family of distributions.  Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.  If there does not exist a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
\end{corollary}
%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

@@

Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to the case of imperfect correctness.

\subsection{Fuzzy min-entropy is not sufficient for secure sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

@@

Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the uniform distribution over all such $W$.  Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. Fix some $4\le t < \gamma$.
We then show the following:

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.  That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
%   More concretely, conditioned on $V=v$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.  For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.  Thus, $\Hav(V| \sketch(V) , Z)$ is small.
\end{itemize}
\begin{proposition} 
\label{prop:each element good} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some fixed $W\in\mathcal{V}$.  The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.  Recall that $t< \gamma$.  We now show that for any $w, w'\in W$, $\dis(w, w') = \gamma$ and thus $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.  Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.  That is, $\dis (w, w')  =\gamma$.
\end{proof}

>>>>

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. 
%The Lincoln Laboratory portion of this work was sponsored by the Department of the Air Force under Air Force Contract \#FA8721-05-C-0002.  Opinions, interpretations, conclusions and recommendations are those of the author and are not necessarily endorsed by the United States Government.  
Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

@@

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item \rep takes an element $w'\in\mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.   
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distinguishability results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.  \bnote{do we care about computational fuzzy extractors?} A fuzzy extractor performs two tasks, information-reconciliation and privacy amplification.  The canonical construction is called \emph{sketch-and-extract:} the uniform key is extracted from $w$~(using a randomness extractor~\cite{nisan1993randomness} and the error-tolerance is obtained by using a secure sketch~\cite[Lemma 4.1]{DBLP:journals/siamcomp/DodisORS08}.  Secure sketches produce a string $ss$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $ss\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $ss\in\{0,1\}^*$.  
\item \emph{Correctness}: $ \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta.$
\item \emph{Security}: for any distribution $W\in\mathcal{W}$, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

@@

\begin{definition}
Let $W$ denote a distribution.  A pair of algorithms, $\sketch, \rec$ is a $(\sketch_W, \rec_W)$ is called a $(\mathcal{M}, W, \tilde{m}, t)$-\emph{distribution-aware secure sketch} if the correctness and security properties hold for the distribution $W$.  That is, 
\begin{enumerate}
\item \emph{Correctness:} 
$
\forall w\in W, \forall w' \in\mathcal{M}| \dis(w',w')\le t, \Pr[\rec(w',\sketch(w))=w]\ge 1-\delta.$
Correctness is guaranteed only for the support of $W$.
\item \emph{Security:} The distribution $W$ is unknown conditioned on $ss$: $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
\end{definition}
The algorithms $(\sketch, \rec)$ know the description of $W$ and security only holds for $W$.  When we consider distribution-aware algorithms, we assume they are \emph{inefficient}.  It would be interesting to investigate natural models for specifying distributions that would allow for efficient~(yet generic) distribution-aware constructions of sketches and extractors.

@@

If an adversary can always obtain the output of a fuzzy extractor by running the reproduce on a fixed point security is impossible~(independent of the implementation of the fuzzy extractor).  We make this intuition formal in the following result.  
For a metric space $\mathcal{M}$, let $\max |\mathcal{M}|$ denote the maximum length required to describe an element $m\in\mathcal{M}$~(for most natural metric spaces this is $\log |\mathcal{M}|$).
\begin{lemma}
\label{lem:fuzz necessary}
Let $n$ be a security parameter and let $W$ be a distribution over $(\mathcal{M}, \dis)$.
If $\Hfuzz (W) = \Theta(\log n)$ there is no $(\mathcal{M}, W, \kappa, t)$-computational fuzzy extractor that is $(\max |\mathcal{M}| +  |\rep|, \epsilon)$-hard for $\epsilon = \ngl(n)$ with error $\delta = \ngl(n)$~(and thus no fuzzy extractor) for $\kappa =\omega(\log n)$.
\end{lemma}

The proof of \lemref{lem:fuzz necessary} is in \apref{sec:proof fuzz necessary}.
Even if we consider a two party protocol where Alice holds $w$ and Bob holds $w'$, 
\lemref{lem:fuzz necessary} still applies.  
This means that fuzzy min-entropy is also a necessary condition for interactive solution.  As described in the introduction, it is possible to provide a common key from $w, w'$ in the interactive setting using secure two party computation.

@@

\noindent We use universal hashes to construct secure sketches for flat distributions.  Skoric et al. previously used universal hash functions to construct secure sketches in the setting of a polynomial number of error patterns~\cite{skoric2009efficient}.

@@

@@

\begin{lemma}
\label{lem:flat hashing}
Let $W$ be a flat distributions with min-entropy $m$.  Then
\consref{cons:universal hash} is a $(\mathcal{M}, W, m - \log |R|, t)$-distribution aware secure sketch with error $\delta \le \frac{|B_{t, max}|-1}{|R|}$. 
\end{lemma}
\begin{proof}
We first argue security.  Fix some $W\in\mathcal{W}$. Since $\mathcal{K}$ and $W$ are independent $\Hav(W | \mathcal{K}) = \Hoo(W) = m$.  Then by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}, $\Hav(W | \mathcal{K}, F(K, W)) \ge \Hoo(W) - \log |F(K, W)| \ge m - \log |R|$.

@@

\noindent Before showing that \consref{cons:leveling} works, we extend our notation for the maximum likelihood ball to the leveled case.  Let $B_{t, i, max}$ be the ball that contains the most points in $L_i$.  That is,
\[
B_{t, i, max} = \max_{w^* \in \mathcal{M}} \{w | w\in W \wedge \dis(w, w^*)\le t \wedge \Pr[W=w]\in L_i\}.
\]
\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  Then \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

We provide a full proof in \apref{sec:proof of layered hashing}.  The argument is similar to the proof of \lemref{lem:flat hashing}, however, there is an additional step showing that releasing the probability information is not too harmful.  Namely, that an adversary with access to the probability information improves their success by a polynomial factor.  Note we release $n$ levels where $n =\log |\mathcal{M}|$.

\end{theorem}
\bnote{right now this is stated without $\ell$.  I found the expression to be really gross with $\ell$ included.  Thoughts?  I know $\ell$ needs to be there because the construction uses it.}

@@

The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.  The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.  The minimax theorem says we can reverse which of these actions is announced first.  That is, the following two player games are equivalent:

%More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively. We provide two formulations of a two player game.\footnote{We denote the outcome of the game as a reward to each player.  This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.  This is to apply results from game theory.}

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing} 
\vspace{.065in}
\end{minipage}  &
\begin{minipage}{3in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
$W \leftarrow \mathcal{W}$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ reward $(1, -1)$\\
Else reward $(-1, 1)$.
\end{tabbing}
\end{minipage}
\end{tabular}
\end{center}

%\begin{center}
%\begin{minipage}{1in}
%\end{center}

%Alternatively, we can think of this as a zero sum game where the adversary wins $1$ and the challenger loses $1$ when the guess is correct with the opposite reward otherwise.
%Instead of using this standard formulation, it will be useful to think of a distribution~(of distributions) over the family $\mathcal{V}$.  This formulation yields the following game:
%In the results that follow it will be useful to think of a different formulation of this game.  Let $\mathcal{W}$ be a distribution~(of distributions) over the family $\mathcal{V}$.

%\begin{center}
%\begin{minipage}{1in}
% \end{minipage} 
%\end{center}

The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms and the adversary specifies a source.  In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.  These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.

\begin{lemma}
\label{lem:quant switch fuzz}
Let $\mathcal{V}$ be a family of distributions.  If for all adversaries $\mathcal{A}$, there Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.  Let $V$ be a distribution over elements of $\mathcal{V}$.  Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$ when the adversary knows the sampled distribution $W$.\footnote{The other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
\end{lemma}

Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.  Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.  We can think of the description of $W$ as side-information or leakage to the adversary.  The system designer, however never sees the particular outcome $W$.  This asymmetry will form the basis of our negative results.

\begin{corollary}
\label{cor:no fuzz for dist}
Let $\mathcal{V}$ be a family of distributions.  Let $V$ be an arbitrary distribution over elements of $\mathcal{V}$.  If there does not exist a $(\mathcal{M}, V, \tilde{m}, t)$-secure sketch on the mixed distribution $V$, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
\end{corollary}
%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

@@

Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to imperfect correctness.

\subsection{Insufficiency of $\Hfuzz(W)$ for distribution-oblivious secure sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, you must be able to design a secure sketch for every distribution over those sources.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

@@

Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\gamma$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \gamma$ and $a_i\neq 0$.  This type of distribution is an affine line in space $\mathbb{F}^\gamma$.  Define $V$ as the uniform distribution over all such $W$.  Furthermore, the side information $Z = a_2, b_2, ..., a_\gamma, b_\gamma$. Fix some $4\le t < \gamma$.
We then show the following~(in \apref{sec:proof secure sketch imposs}):

\begin{itemize}
\item \propref{prop:each element good}: for all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item \propref{prop:distribution uniform}: the distribution $V$ is uniform~(from the sketch designer's point of view).  That is $V\overset{d}=U$.
\item \lemref{lem:secure sketch entropy loss}: for any secure sketch on $V$, the support size of $V | \sketch(V)$ decreases significantly.
\item \lemref{lem:side info determines sketch}:  for most auxiliary information $Z$, there are few possible values of $V|Z$ in the support of $V | \sketch(V)$.  That is, $\tilde{H}_0(V | \sketch(V), Z) = \Theta(1)$.
\end{itemize}
\end{proof}
\subsubsection{Feasibility of computational secure sketches}
Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.  %This means that ruling out any information-theoretic secure sketches also rules out a computational secure sketch.  
The definitional of Fuller et al. is uses a weak version of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} due to Gentry and Wichs~\cite{gentry2011separating}.
